### 2018-02-22 thesis/contents/tn_sagit.tex

\subsubsection{Along-the-tract Analysis}
Tractography centroids, which were the average curve best fit the tract bundle, were identified on the merged tracts in template space. The spline was then resampled into 30 points and became the centroid definition. Nearest-neighbor point assignment was used to divide the merged tract into 30 cross sections along the centroids. Diffusion metrics from the tractography points were averaged for each of the cross-sections. CN V centroids were manually defined using 3 control points. A Catmull-Rom spline \cite{DeRose1988} was then defined from these control points using the VTK software library \cite{Schroeder2005}. TPT and S1 centroids were defined using QuickBundles \cite{Garyfallidis2012} with distance threshold of 30.

>>>>

\subsubsection{Along-the-tract Analysis}
Tractography centroids, which were the average curve best fit the tract bundle, were identified on the merged tracts in template space. The spline was then resampled into 30 points and became the centroid definition. Nearest-neighbor point assignment was used to divide the merged tract into 30 sections along the centroid. Diffusion metrics from the tractography points were averaged for each of the sections. CN V centroids were manually defined using 3 control points. A Catmull-Rom spline \cite{DeRose1988} was then defined from these control points using the VTK software library \cite{Schroeder2005}. TPT and S1 centroids were defined using QuickBundles \cite{Garyfallidis2012} with distance threshold of 30.

\begin{figure}[ht]
\centering
\includegraphics[width=\linewidth]{thesis/images/tn-gp-sagit/figure-path-analysis.pdf}
\caption{Diagram for the along-the-tract data processing.}
\label{fig:GPfigure-method-centroid}
\end{figure}
